Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-05 paper/content/inverted_u.tex
small update
better eeog fig

Figure \ref{eq_regret} displays the \swedit{market regret (average
  over multiple runs)} under different levels of competitions,
assuming both firms playing their equilibrium strategies. Consumer
welfare is \textit{better off} in the temporary monopoly case than in
the duopoly case. However, this was expected from the fact that the
incumbent is incentivized to play \TS. The welfare in the temporary
monopoly case is close to the welfare to having a single firm playing
\TS.

\swedit{We also observe that monopoly and duopoly achieve similar
  welare, with monopoly being marginally better than duopoly. This is
  surprising since one might conjecture that the welfare should
  increase with the number of firms playing \DG since more $\DG$ runs
  should result in faster concentration on playing the better arms. In
  particular,, more firms playing \DG should result in faster
  discovery of a better arm, and the firm with such discovery would be
  able to attract more consumers and increase market welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase the number of firms playing \DG}
\label{many_firm_welfare}
\end{figure}

>>>>

Figure \ref{eq_regret} displays the \swedit{market regret (average
  over multiple runs)} under different levels of competitions,
assuming both firms playing their equilibrium strategies. Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. However, this was expected from the fact that the incumbent is incentivized to play \TS. The welfare in the temporary monopoly case is close to the welfare to having a single firm playing
\TS.

\swedit{We also observe that monopoly and duopoly achieve similar
  welfare, with monopoly being marginally better than duopoly. This is
  surprising since one might conjecture that the welfare should
  increase with the number of firms playing \DG since more $\DG$ runs
  should result in faster concentration on playing the better arms. In
  particular,, more firms playing \DG should result in faster
  discovery of a better arm, and the firm with such discovery would be
  able to attract more consumers and increase market welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase the number of firms playing \DG}
\label{many_firm_welfare}
\end{figure}
